TacticToe: Learning the Game of Tactics

### 2018-01-16 tactictoe_jv.tex
Proof presentation: update

\section{Introduction}\todo{TG + JU + CK}
%\begin{example} Proof automatically generated by \tactictoe for the user given 
%goal
%\small
%\begin{center}
%
%
%\begin{BVerbatim}[commandchars=\\\{\}]
%Goal: ``\(\forall\)l. FOLDL (\(\lambda\)xs x. SNOC x xs) [] l = l``
%Proof:
%  SNOC_INDUCT_TAC THENL
%  [ REWRITE_TAC [APPEND_NIL, FOLDL],
%    ASM_REWRITE_TAC [APPEND_SNOC, FOLDL_SNOC]
%      THEN CONV_TAC (DEPTH_CONV BETA_CONV)
%      THEN ASM_REWRITE_TAC [APPEND_SNOC, FOLDL_SNOC] ]
%\end{BVerbatim}
%
%
%\end{center}
%
%\end{example}
%
\vspace{100mm}

\tableofcontents

@@

\paragraph{Minimizing length and time of the proof} 
First a weak minimization is possible when processing the final proof. If the 
tactic \texttt{A THEN B} appears in the proof and has the same effect as 
\texttt{B} then we can drop \texttt{A} from the proof.
Stronger minimization can be obtained by rerunning the prover with feature 
vectors containing only tactics 
from the proof. To obtain a shorter proof, the diagonalization coefficient is
reduced to encourage exploration in the width of the proof tree. Similarly by 
ponderating each tactic application by its time and setting the 
diagonalization  coefficient is set to a tenth of the timeout of a tactic, we 
can aim for faster proofs.

\paragraph{Minimizing tactic arguments}
One of the argument that may contain unnecessary information are lists.
We test if the minimized tactic has the same effect as the original one.
This is a generalization of the simplest method used for minimizing a list of 
theorems in ``hammers'' \cite{}. The fact that the lists are generally small 
make this approach feasible.

>>>>

\section{Introduction}\todo{TG + JU + CK}
%\begin{example} Proof automatically generated by \tactictoe for the user given 
%goal
%\small
%\begin{center}
%
%
%\begin{BVerbatim}[commandchars=\\\{\}]
%Goal: ``\(\forall\)l. FOLDL (\(\lambda\)xs x. SNOC x xs) [] l = l``
%Proof:
%  SNOC_INDUCT_TAC THENL
%  [ REWRITE_TAC [APPEND_NIL, FOLDL],
%    ASM_REWRITE_TAC [APPEND_SNOC, FOLDL_SNOC]
%      THEN CONV_TAC (DEPTH_CONV BETA_CONV)
%      THEN ASM_REWRITE_TAC [APPEND_SNOC, FOLDL_SNOC] ]
%\end{BVerbatim}
%
%
%\end{center}
%
%\end{example}
%
\vspace{100mm}
\tableofcontents

@@

\paragraph{Minimizing length and time of the proof} 
First a weak minimization is possible when processing the final proof. If the 
tactic \texttt{A THEN B} appears in the proof and has the same effect as 
\texttt{B} then we can drop \texttt{A} from the proof.
Stronger minimization can be obtained by rerunning the prover with feature 
vectors containing only tactics 
from the proof. To obtain a shorter proof, the exploration coefficient should be
increased and the policy coefficient lowered to encourage exploration in the 
width of the proof tree. Additionally, by giving a weaker evaluation to slow 
tactics, we can aim for faster proofs.

\paragraph{Minimizing tactic arguments}
One of the argument that may contain unnecessary information are lists.
Let $t$ be a tactic applied to a goal $g$ containing a list $l$ as argument. 
And let $t'$ be the tactic $t$ where one element $e$ of $l$ as be removed. If 
$t$ and $t'$ have the same effect on $g$ then $t'$ can replace $t$ in the final 
proof.

This is a generalization of the simplest method used for minimizing a list of 
theorems in ``hammers'' \cite{}. The fact that lists are generally small
make this approach feasible.
